---
title: "_longevityTools_: analysis tools for longevity research" 
author: "Authors: Thomas Girke, Danjuma Quarless, Kuan-Fu Ding, Jamison McCorrison, Tyler Backman, Nik Schork, Dan Evans"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 3
    fig_caption: yes

fontsize: 14pt
bibliography: bibtex.bib
---
<!--
%% \VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Overview Vignette}
%% \VignetteDepends{methods}
%% \VignetteKeywords{compute cluster, pipeline, reports}
%% \VignettePackage{longevityTools}
-->

<!---
- Compile from command-line
echo "rmarkdown::render('longevityTools.Rmd')" | R -slave; R CMD Stangle longevityTools.Rmd

- Commit to github
git commit -am "some edits"; git push -u origin master

- To customize font size and other style features, add this line to output section in preamble:  
    css: style.css
-->

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE, messages=FALSE, warnings=FALSE}
suppressPackageStartupMessages({
    library(longevityTools) 
    library(ggplot2) }) 
```

Note: the GitHub repository of this package is <a href="https://github.com/tgirke/longevityTools">here</a> and the most recent version of this tutorial can be found <a href="https://htmlpreview.github.io/?https://github.com/tgirke/longevityTools/blob/master/vignettes/longevityTools.html">here</a>.

# Introduction 
text text text text text text text text text text text text
text text text text text text text text text text text text
text text text text text text text text text text text text
text text text text text text text text text text text text
some citation [@Li2013-oy; @Li2009-oc]

<div align="right">[Back to Table of Contents]()</div>


# Getting Started

## Installation

The R software for running [_`longevityTools`_](https://github.com/tgirke/longevityTools) can be downloaded from [_CRAN_](http://cran.at.r-project.org/). The _`longevityTools`_ package can be installed from the R console using the following _`biocLite`_ install command. 

```{r install, eval=FALSE}
source("http://bioconductor.org/biocLite.R") # Sources the biocLite.R installation script 
biocLite("tgirke/longevityTools", build_vignettes=TRUE, dependencies=TRUE) # Installs package from GitHub
```
<div align="right">[Back to Table of Contents]()</div>

## Loading package and documentation

```{r documentation, eval=FALSE}
library("longevityTools") # Loads the package
library(help="longevityTools") # Lists package info
vignette("longevityTools") # Opens vignette
```
<div align="right">[Back to Table of Contents]()</div>

## Sample data from GTEx
The eQTL data used in this vignette can be downloaded from the [GTEx site](http://www.gtexportal.org/home/datasets).
Note, the following downloads a 1.3GB file, which will take some time.

```{r eQTL_download, eval=FALSE}
download.file("http://www.gtexportal.org/static/datasets/gtex_analysis_v6/single_tissue_eqtl_data/GTEx_Analysis_V6_eQTLs.tar.gz", "./GTEx_Analysis_V6_eQTLs.tar.gz")
untar("GTEx_Analysis_V6_eQTLs.tar.gz")
```

## Utilities
The _`geneGrep`_ function takes GTEx results and gene list as arguments,
returns GTEx eSNP results for genes in gene list. Genes without significant
eSNPs are removed from results. The following sample file _Whole\_Blood\_Analysis.snpgenes_ 
has been subsetted to the first 100 rows.
```{r geneGrep, eval=TRUE}
library(longevityTools)
samplepath <- system.file("extdata", "Whole_Blood_Analysis.snpgenes.head100", package="longevityTools") 
dat <- read.delim(samplepath)
myGenes <- c("RP11-693J15.4", "RP11-809N8.4", "junkNoMatch")
result <- geneGrep(dat, myGenes)
result
```

<div align="right">[Back to Table of Contents]()</div>


# Version information

```{r sessionInfo}
sessionInfo()
```
<div align="right">[Back to Table of Contents]()</div>

# References
