---
title: "_longevityTools_: analysis tools for longevity research" 
author: "Author: Thomas Girke (thomas.girke@ucr.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 3
    fig_caption: yes

fontsize: 14pt
bibliography: bibtex.bib
---
<!--
%% \VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Overview Vignette}
%% \VignetteDepends{ggplot2}
%% \VignetteKeywords{compute cluster, pipeline, reports}
%% \VignettePackage{longevityTools}
-->

<!---
- Compile from command-line
echo "rmarkdown::render('longevityTools.Rmd')" | R -slave; R CMD Stangle longevityTools.Rmd

- Commit to github
git commit -am "some edits"; git push -u origin master

- To customize font size and other style features, add this line to output section in preamble:  
    css: style.css
-->

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE, messages=FALSE, warnings=FALSE}
suppressPackageStartupMessages({
    library(longevityTools)
    library(ggplot2)
})
```

Note: the most recent version of this tutorial can be found <a href="https://htmlpreview.github.io/?https://github.com/tgirke/systemPipeR/blob/master/vignettes/systemPipeR.html">here</a> and a short overview slide show [here](https://htmlpreview.github.io/?https://github.com/tgirke/systemPipeR/master/inst/extdata/slides/systemPipeRslides.html).

# Introduction
text text text text text text text text text text text text
text text text text text text text text text text text text
text text text text text text text text text text text text
text text text text text text text text text text text text
some citation [@Li2013-oy; @Li2009-oc]

<div align="right">[Back to Table of Contents]()</div>


# Getting Started

## Installation

The R software for running [_`longevityTools`_](https://github.com/tgirke/longevityTools) can be downloaded from [_CRAN_](http://cran.at.r-project.org/). The _`longevityTools`_ package can be installed from the R console using the following _`biocLite`_ install command. 

```{r install, eval=FALSE}
source("http://bioconductor.org/biocLite.R") # Sources the biocLite.R installation script 
biocLite("tgirke/longevityTools", build_vignettes=TRUE, dependencies=TRUE) # Installs package from GitHub
```
<div align="right">[Back to Table of Contents]()</div>

## Loading package and documentation

```{r documentation, eval=FALSE}
library("longevityTools") # Loads the package
library(help="longevityTools") # Lists package info
vignette("longevityTools") # Opens vignette
```
<div align="right">[Back to Table of Contents]()</div>

## Utilities
The _`geneGrep`_ function takes GTEx results and gene list as arguments,
returns GTEx eSNP results for genes in gene list. Genes without significant
eSNPs are removed from results. Input data: GTEx_Analysis_V6_eQTLs.tar.gz 

```{r genRna_workflow, eval=FALSE}
library(longevityTools)
dat <- read.table("~/Documents/longevity/GTEx/data/Whole_Blood_Analysis.snpgenes.head100", header=TRUE, sep="\t", stringsAsFactors=FALSE)
myGenes<- c("RP11-693J15.4", "RP11-809N8.4", "junkNoMatch")
result <- geneGrep(dat, myGenes)
```

<div align="right">[Back to Table of Contents]()</div>


# Version information

```{r sessionInfo}
sessionInfo()
```
<div align="right">[Back to Table of Contents]()</div>

# References
