---
title: "_longevityTools_: Connecting Age-related Gene Expression Signatures with Small Molecules" 
author: "Authors: Thomas Girke, Danjuma Quarless, Kuan-Fu Ding, Jamison McCorrison, Tyler Backman, Nik Schork, Dan Evans"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 3
    fig_caption: yes

fontsize: 14pt
bibliography: bibtex.bib
---
<!--
%% \VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Overview Vignette}
%% \VignetteDepends{methods}
%% \VignetteKeywords{compute cluster, pipeline, reports}
%% \VignettePackage{longevityTools}
-->

<!---
- Compile from command-line
echo "rmarkdown::render('longevityTools_CMAP.Rmd')" | R -slave; R CMD Stangle longevityTools_CMAP.Rmd

- Commit to github
git commit -am "some edits"; git push -u origin master

- To customize font size and other style features, add this line to output section in preamble:  
    css: style.css
-->

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE, messages=FALSE, warnings=FALSE}
suppressPackageStartupMessages({
    library(longevityTools) 
    library(ggplot2) }) 
```

Note: the GitHub repository of this package is <a href="https://github.com/tgirke/longevityTools">here</a> and the most recent version of this tutorial can be found <a href="https://htmlpreview.github.io/?https://github.com/tgirke/longevityTools/blob/master/vignettes/longevityTools_CMAP.html">here</a>.

# Introduction 
text text text text text text text text text text text text
text text text text text text text text text text text text
text text text text text text text text text text text text
text text text text text text text text text text text text
some citation [@Li2013-oy; @Li2009-oc]

<div align="right">[Back to Table of Contents]()</div>


# Getting Started

## Installation

The R software for running [_`longevityTools`_](https://github.com/tgirke/longevityTools) can be downloaded from [_CRAN_](http://cran.at.r-project.org/). The _`longevityTools`_ package can be installed from the R console using the following _`biocLite`_ install command. 

```{r install, eval=FALSE}
source("http://bioconductor.org/biocLite.R") # Sources the biocLite.R installation script 
biocLite("tgirke/longevityTools", build_vignettes=TRUE, dependencies=TRUE) # Installs package from GitHub
```
<div align="right">[Back to Table of Contents]()</div>

## Loading package and documentation

```{r documentation, eval=FALSE}
library("longevityTools") # Loads the package
library(help="longevityTools") # Lists package info
vignette("longevityTools_CMAP", package="longevityTools") # Opens vignette
```
<div align="right">[Back to Table of Contents]()</div>

## Sample data from GTEx
The eQTL data used in this vignette can be downloaded from the [GTEx site](http://www.gtexportal.org/home/datasets).
Note, the following downloads a 1.3GB file, which will take some time.

```{r source_fct, eval=TRUE}
fctpath <- system.file("extdata", "analysis_Fct.R", package="longevityTools")
source(fctpath)
```

## Download data from Connectivity Map project site
The data were downloaded from CMAP web site [here](http://www.broadinstitute.org/cmap). The 
`getCmap` function downloads the rank matrix and the compound annotation files, while `getCmapCEL`
downloads the corresponding 7,056 CEL files. The functions will write the data to a `data` directory
within the present workding directory of R session. This `data` directory plus a `data/CEL` directory
needs to be generated by the user prior to running the download functions.
```{r download_cmap, eval=TRUE}
getCmap(rerun=FALSE) # Downloads cmap rank matrix and compound annotation files
getCmapCEL(rerun=FALSE) # Download cmap CEL files. Note, this will take some time
```

<div align="right">[Back to Table of Contents]()</div>


# Version information

```{r sessionInfo}
sessionInfo()
```
<div align="right">[Back to Table of Contents]()</div>

# References
