---
title: "_longevityTools_: Analysis Tools for Longevity Research" 
author: "Authors: Thomas Girke, Danjuma Quarless, Tyler Backman, Kuan-Fu Ding, Jamison McCorrison, Nik Schork, Dan Evans"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 3
    fig_caption: yes

fontsize: 14pt
bibliography: bibtex.bib
---
<!--
%% \VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Overview Vignette}
%% \VignetteDepends{methods}
%% \VignetteKeywords{compute cluster, pipeline, reports}
%% \VignettePackage{longevityTools}
-->

<!---
- Compile from command-line
echo "rmarkdown::render('longevityTools.Rmd')" | R -slave; R CMD Stangle longevityTools.Rmd

- Commit to github
git commit -am "some edits"; git push -u origin master

- To customize font size and other style features, add this line to output section in preamble:  
    css: style.css
-->

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
options(width=100, max.print=1000)
knitr::opts_chunk$set(
    eval=as.logical(Sys.getenv("KNITR_EVAL", "TRUE")),
    cache=as.logical(Sys.getenv("KNITR_CACHE", "TRUE")))
```

```{r setup, echo=FALSE, messages=FALSE, warnings=FALSE}
suppressPackageStartupMessages({
    library(longevityTools) 
    library(ggplot2) }) 
```

Note: the GitHub repository of this package is <a href="https://github.com/tgirke/longevityTools">here</a> and the most recent version of this tutorial can be found <a href="https://htmlpreview.github.io/?https://github.com/tgirke/longevityTools/blob/master/vignettes/longevityTools.html">here</a>.

# Introduction 
This vignette provides general information about the `longevityTools` package.
Its development is part of the [Longevity Genomics](http://www.longevitygenomics.org/) project. 
The analysis workflows used by this project are documented in companion vignettes. Currently, 
this includes the [longevityTools_eQTL](https://htmlpreview.github.io/?https://github.com/tgirke/longevityTools/blob/master/vignettes/longevityTools_eQTL.html) and
[longevityTools_CMAP](https://htmlpreview.github.io/?https://github.com/tgirke/longevityTools/blob/master/vignettes/longevityTools_CMAP.html) 
vignettes [@Li2013-oy; @Li2009-oc].

<div align="right">[Back to Table of Contents]()</div>


# Getting Started

## Installation

The R software for running [_`longevityTools`_](https://github.com/tgirke/longevityTools) can be downloaded from [_CRAN_](http://cran.at.r-project.org/). The _`longevityTools`_ package can be installed from the R console using the following _`biocLite`_ install command. 

```{r install, eval=FALSE}
source("http://bioconductor.org/biocLite.R") # Sources the biocLite.R installation script 
biocLite("tgirke/longevityTools", build_vignettes=TRUE, dependencies=TRUE) # Installs package from GitHub
```
<div align="right">[Back to Table of Contents]()</div>

## Loading package and documentation

```{r documentation, eval=FALSE}
library("longevityTools") # Loads the package
library(help="longevityTools") # Lists package info
vignette("longevityTools") # Opens vignette
```

## Overview of object clases, methods and functions
To be added later...

<div align="right">[Back to Table of Contents]()</div>

# Version information

```{r sessionInfo}
sessionInfo()
```
<div align="right">[Back to Table of Contents]()</div>

# Funding
This project is funded by NIH grant U24AG051129 awarded by the National Intitute of Aging (NIA).

<div align="right">[Back to Table of Contents]()</div>

# Version information

<div align="right">[Back to Table of Contents]()</div>

# References
